Human Factors Influencing Visual Statistical Inference

### 2013-06-09 sociology_paper.tex
resuls section updated

To meet the Institutional Regulatory Board (IRB) requirement, it is necessary to exclude any subject less than 18 years of old to participate human subject experiment. Thus we intend to only focus on the performance of observer with age 18 years or older. We don't expect many older people to participate our study and we are interested of age from 18 to 65 years.

@@

Most of the participants are graduate degree holder. They are mostly from India as any university degree is considered a graduate degree unlike north America where graduate degree means Masters level education. This is apparent in Figure \ref{fig:demographic_info}. Most of the unites states participants are with an Undergraduate degree or at least have some undergraduate course.

@@

We observed some variations in median proportion of correct responses for different levels of the demographic factors as in Figure \ref{fig:demographic_effect}. But the variability of proportion correct responses are huge as per design of the experiments since we have some easy and some difficult lineups. There were lineups which were not expected to be evaluated correctly and some were very easy and expected to be evaluated correctly 100\% of the time.

@@

%------------------------------------------------------------------------------------
\paragraph{Acknowledgments}
%------------------------------------------------------------------------------------
This work was funded in part by National Science Foundation grant DMS 1007697. All studies were conducted with approval from the internal review board IRB 10-347.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_bar.pdf} 
   \caption{Countrywise distribution of age and academic levels of the MTurk workers participating the experiments shows the diversity of the subjects in all the demographic aspect. Male and female participants differ in India specially for agelevel 18-25. For United States number of participants are similar beyond age 40 while few number of participants coming from India beyond that age.}
   \label{fig:gender_country}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_time.pdf} 
   \caption{Countrywise average time taken for different age and academic levels of the MTurk workers participating the experiments shows that the demographic factors may not have effect on time taken. }
   \label{fig:gender_country}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_correct.pdf} 
   \caption{Countrywise percentage of correct responses for different age and academic levels of the MTurk workers participating the experiments shows that the demographic factors may not have effect on the percentage of correct responses. }
   \label{fig:gender_country}
\end{figure}

>>>>

To meet the Institutional Review Board (IRB) requirement, it is necessary to exclude any subject less than 18 years of old to participate human subject experiment. Thus we intend to only focus on the performance of observer with age 18 years or older. We don't expect many older people to participate our study and we are interested of age from 18 to 65 years.

@@

Most of the participants are graduate degree holder. They are mostly from India as any university degree is considered a graduate degree unlike north America where graduate degree means Masters level education. This is apparent in Figure \ref{fig:demographic_info}. Most of the unites states participants are with an Undergraduate degree or at least have some undergraduate courses.

Male and female participants are similarly distributed among all age groups except age 18-25 in India where less female participants were observed as we see in Figure \ref{fig:gender_country_bar}. Most of the participants from India are below age 40 while in United States the distribution of participants are similar beyond age 40.

A total of XX lineups were evaluated in all these 10 experiments. Each person was supposed to evaluate 10 lineups except experiment 9 where three lineups were evaluated by each person. To clean the data we used the test plot as the basis and did not include the results of that test plot. In some cases the demographic information were not provided by the participants. Also, for some ip address, the actual geographical locations could not be retrieved. This resulted some missing demographic information.

@@

We observed some variations in median proportion of correct responses for different levels of the demographic factors as in Figure \ref{fig:demographic_effect}. But the variability of proportion correct responses are huge as per design of the experiments since we have some easy and some difficult lineups. There were lineups which were not expected to be evaluated correctly and some were very easy and expected to be evaluated correctly 100\% of the time. This is why we see the boxes ranges from 0 to 1 in most of the factor levels.

The averages of proportion correct are for different factor levels are shown as dots in Figure \ref{fig:demographic_effect}. Unlike median, less variations are observed in the averages for different factor levels. As expected, there is no significant difference between Male and female performances. Among all the demographic factor levels only graduate degree, India and age group 31-35 appear to be significantly different from others. Most of the Indian participants reported to have a graduate degree. Thus the effect of graduate degree is actually the effect of India.

@@

%------------------------------------------------------------------------------------
\paragraph{Acknowledgments}
%------------------------------------------------------------------------------------
This work was funded in part by National Science Foundation grant DMS 1007697. All studies were conducted with approval from the Institutional Review Board IRB 10-347.

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_bar.pdf} 
   \caption{Countrywise distribution of age and academic levels of the MTurk workers participating the experiments shows the diversity of the subjects in all the demographic aspect. Male and female participants differ in India specially for agelevel 18-25. For United States number of participants are similar beyond age 40 while few number of participants coming from India beyond that age.}
   \label{fig:gender_country_bar}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_time.pdf} 
   \caption{Countrywise average time taken for different age and academic levels of the MTurk workers participating the experiments shows that the demographic factors may not have effect on time taken. }
   \label{fig:gender_country_time}
\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{age_gender_within_country_correct.pdf} 
   \caption{Countrywise percentage of correct responses for different age and academic levels of the MTurk workers participating the experiments shows that the demographic factors may not have effect on the percentage of correct responses. }
   \label{fig:gender_country_response}
\end{figure}
